% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
\documentclass[runningheads]{llncs}

\usepackage{graphicx}
\graphicspath{{images/}}
\usepackage{todonotes}
\usepackage{float}

% Necessary to be able to use urls in the bib file
\usepackage{url}

% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

%
% Extra commands for references
%
\newcommand{\appendixref}[1]{Appendix~\ref{#1}}
\newcommand{\figureref}[1]{Figure~\ref{#1}}
\newcommand{\sectionref}[1]{Section~\ref{#1}}
\newcommand{\subsectionref}[1]{Subsection~\ref{#1}}
\newcommand{\chapterref}[1]{Chapter~\ref{#1}}
\newcommand{\tableref}[1]{Table~\ref{#1}}
\newcommand{\formularef}[1]{Formula~\ref{#1}}

\begin{document}

\title{An approach for continuous painting detection and room prediction during a museum walk}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{
    Thomas Aelbrecht \and
    Andreas De Witte \and
    Jochen Laroy \and
    Pieter-Jan Philips \and
    Gillis Werrebrouck
}

% The short form of the title
\titlerunning{Continuous painting detection in a museum}

% The short form of the authors
\authorrunning{T. Aelbrecht et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Ghent University, Valentin Vaerwyckweg 1, 9000 Ghent, Belgium}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}

Are you tired of exploring a museum on a map and figuring out where you are? This paper focusses on resolving this issue. It allows the detection of paintings in a video or on a live recording while walking through the museum. The paintings are detected using a mean-shift segmentation filter, floodfilling and contour detection. The detected paintings are matched against all known paintings in the museum and a couple of predictions are made. These predictions are then used as input for an model inspired by the Hidden Markov model which determines if the given predictions are possible and don't cause a teleportation through the museum. All information is displayed on a clear map so it's easy to know where you are in the museum. Never look at the map again, look at your phone while enjoying the paintings!

\keywords{Painting detection \and Painting matching \and Painting mask \and Hidden Markov model}
\end{abstract}
%

% TODO: content here
\input{chapters/Introduction}
\input{chapters/Assignment1}
\input{chapters/Assignment2}
\input{chapters/Assignment3}
\input{chapters/Assignment4}
\input{chapters/Assignment5}

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% TODO: is the style really necessary?
\bibliographystyle{splncs04}
\bibliography{references}

\end{document}
